Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-28 paper/paper.Rmd
writing evd methods

Given our interest in the tail-end of the seed dispersal kernels and our focus on the occurrence of long-distance events, we decided to use an extreme value theory approach and fit a Generalized Pareto distribution to the dispersal distances above the 500m threshold established.

>>>>

Given our interest in the tail-end of the seed dispersal kernels and our focus on the occurrence of long-distance events, we decided to use an extreme value theory approach and fit a Generalized Pareto distribution to the dispersal distances above the 500m threshold established. Statistics of extremes are useful to understand the stochastic behavior of rare extreme events [@coles2001introduction] and have previously been used in ecological scenarios [@gaines1993largest; @katz2005statistics] and evolutionary genetics [@beisel2007testing; @joyce2008general]. More recently, statistics of extremes have been used to model extended dispersal kernels of seeds and pollen [@garcia_extended_2017] and in particular have been proposed to understand long-distance dispersal events [@rogers_total_2019]. In our particular case, we were interested to evaluate how an approach using statistics of extremes could help us fit the tail of the frugivore-generated seed dispersal kernels for each of the models we simulated. We used a peak over threshold (POT) approach, in which we filtered the dispersal distances above a given threshold and fit a Generalized Pareto (GP) distribution to those values. This differs from a block maxima (BM) approach, where the maximum value is selected for each sampling unit and a Generalized Extreme Value (GEV) distribution is used, therefore the choice in the approach is determined by the structure in sampling for a given study (further details can be found in [@coles2001introduction; @garcia_extended_2017]).

<!-- Describe the density functions for both distributions, how they are related and what information is given by their parameters  -->

Our study focused on long-distance dispersal events defined as any dispersal event over 500m from the parent tree in order to compare our results to previous studies in this same ecological system [@holbrook_dispersal_2009; @holbrook_home_2011; @holbrook_using_2007]. However, when selecting a threshold for a POT approach, it is also possible to use diagnostic plots by fitting the data to a sequence of thresholds, with the goal of finding the lowest threshold that provides similar parameter values to any other higher threshold. We performed these analysis (Supplementary information), and given that parameter estimates were similar, we report our parameter estimates and probability estimates of long-distance events using our original 500m threshold.
